A new method to estimate dark matter halo concentrations

### 2015-02-23 paper/article.tex
finished solving minor issues

\subsection{Integrated Mass}
From these definitions we can compute the total mass enclosed inside a
radius $r$:
\begin{equation}
M(<r) = 4\pi\rho_c\delta_c  r_s^3\left[\ln \left
  (\frac{r_s+r}{r}\right) - \frac{r}{r_s+r}\right].
\end{equation}

@@

\begin{equation}
\mathrm{max}(v(<x)) = \sqrt{\frac{c}{x_{\rm max}}\frac{f(x_{\rm
      max})}{f(c)}},
\label{eq:max_v}
\end{equation}
where $x_{\rm max}=2.163$ and the function $f(x)$ was defined in Eq. (\ref{eq:f_NFW}).

@@

We generate in total $400$ mock halos split into four different
groups of $100$ halos each.
The four groups differ in the total number of particles for their halos:
$20$, $200$, $2000$ and $20000$.
Inside each group the halos have random concentration values in
the range $1<c<20$ with a flat distribution.
For all these halos with find the concentration values using the
density, velocity and mass methods described in the previous
section. We quantify the difference between the expected $c_{in}$
and obtained $c_{out}$ values by

@@

We build a sample of all halos located in a cubic sub-volume of $100$
\hMpc on a side centered on the most massive halo in the simulation at
$z=0$ which corresponds to the \texttt{miniMDR1} tables in the
database.
From this sample we select all the halos at $z=0$ detected with a
Friends-of-Friends (FoF) algorithm with masses in the interval
$10^{11}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$.
The FoF algorithm used with a linking length of $0.17$ times the average
inter-particle distance. This choice translates into an overdensity
$\Delta_h\sim 400-700$ dependent on the halo concentration
\citep{More2011}.
Finally, for each FoF halo we select from all the particles that
belong to it.

>>>>

\subsection{Integrated Mass}
From these definitions we can compute the total mass enclosed inside a
radius $r$:
\begin{equation}
M(<r) = 4\pi\rho_c\delta_c  r_s^3\left[\ln \left
  (\frac{r_s+r}{r_s}\right) - \frac{r}{r_s+r}\right].
\end{equation}

@@

\begin{equation}
\mathrm{max}(v(<x)) = \sqrt{\frac{c}{x_{\rm max}}\frac{f(x_{\rm
      max})}{f(c)}},
\label{eq:max_v}
\end{equation}
where $x_{\rm max}=2.163$ \citep{Klypin2014} and the function $f(x)$
was defined in Eq. (\ref{eq:f_NFW}).

@@

We generate in total $400$ mock halos split into four different
groups of $100$ halos each.
The four groups differ in the total number of particles for their halos:
$20$, $200$, $2000$ and $20000$.
Inside each group the halos have random concentration values in
the range $1<c<20$ with a uniform distribution.
For all these halos with find the concentration values using the
density, velocity and mass methods described in the previous
section. We quantify the difference between the expected $c_{in}$
and obtained $c_{out}$ values by

@@

We build a sample of all halos located in a cubic sub-volume of $100$
\hMpc on a side centered on the most massive halo in the simulation at
$z=0$ which corresponds to the \texttt{miniMDR1} tables in the
database.
From this sample we select all the halos at $z=0$ detected with a
Friends-of-Friends (FoF) algorithm with masses in the interval
$10^{11}\leq M_{\rm FoF}/\hMsun \leq 10^{15}$.
The FoF algorithm used with a linking length of $0.17$ times the average
inter-particle distance. This choice translates into an overdensity
$\Delta_h\sim 400-700$ dependent on the halo concentration
\citep{More2011}.
Finally, for each FoF halo we select all the particles that
belong to it.
